---
title: "cv_plot"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{cv_plot}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(simodiff)
```

The efficiency of the resamples in the bootstrap simulations was analyzed graphically using the number of resamples *versus* the coefficient of variation *CV*. The *CV* was calculated for the cumulative resamples of each model, with the cumulative values increasing after every $n_{i}$ data point.

$$cv = sd(x)/mean(x)*100$$
where *x* represents the vector of bootstrapped values and *sd* denotes the standard deviation.

## Arguments

The arguments in the function are as follows:

    df      A data frame containing two columns: Factors and X. The X column represents the vector of bootstrapped values for analysis.
    ni      An integer represents the starting value of the cumulative series.
    B       An integer that determines the number of resamplings.
    nb      An integer indicates the increasing number of the cumulative series.
    x_label A character vector with the label for the X-axis.
    y_label A character vector with the label for the y-axis.

## Returns

The function returns a plot of *CV* results against the cumulative number of iterations for each model.

## import

ggplot2 tidyr

## Example

```{r, eval = FALSE}
# Generate the sample
# Set seed for reproducibility
set.seed(16) # Set seed for reproducibility

n <- 1000  # Sample size
mean_1 <- 10  # Mean of the distribution
sd_1 <- 3  # Standard deviation of the distribution
sample_1 <- rnorm(n, mean_1, sd_1)

mean_2 <- 15  # Mean of the distribution
sd_2 <- 2  # Standard deviation of the distribution
sample_2 <- rnorm(n, mean_2, sd_2)

X <- rbind(sample_1,sample_2) # bind resampled values in one vector
Factor <- as.factor(rep(c("sample_1","sample_2"), each=n))

df <- data.frame(Factor,X= as.numeric(X))

# Axes labels
x_label <- "Cummulative iterations"
y_label <- "CV%"

ni <- 50
B <- n
nb <- 50

cv_plot <- cv_out(df,ni,B,nb, x_label, y_label)
cv_plot 

```

## The function

```{r}
cv_plot <- function(df,ni,B,nb, x_label, y_label){
  # Create an empty data frame to store the results `cv_out`.
  r_names <- levels(df$Factor) # row names
  grp <- seq(ni,B,by=nb)  # Defining the range of accumulated values.
  cv_out <- data.frame(matrix(NA,nrow=length(grp),ncol=length(r_names)+1))
  colnames(cv_out ) <- c("X",as.character(r_names))
  cv_out$X <- grp

  # Calculate the cumulative coefficient of variation (CV) of L50 for the B
  # resamples for each model.

  for(i in 1:length(r_names)){
    tmp <- filter(df, .data$Factor == as.character(r_names[i]),)
    for(j in 1:length(grp)){
      x <- tmp[,2]
      xj <- x[c(1:grp[j])]
      cv_out[j,i+1] <- (sd(xj) / mean(xj)) * 100
    }
  }
  # Transforming the data set into a tidy format.
  tmp <- cv_out %>%
    pivot_longer(!.data$X, names_to="model", values_to = "cv")

  # Plotting the coefficient of variation (CV) results against the cumulative number
  # of iterations for each model.
  p <- ggplot(tmp, aes(x= .data$X, y= as.numeric(.data$cv))) +
    scale_linetype_binned()+
    geom_line(aes(x= .data$X, y= as.numeric(.data$cv), lty = 1)) +
    labs(x= x_label, y= y_label) +
    facet_wrap(~factor(as.factor(model), levels= unique(model)))
  print(p)
}
```


