---
title: "fit_models"
subtitle: "Fitting model for every database"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fit_models}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(simodiff)
```

All sigmoid models are fitted using the `optim()` function for each data set. Each
model is evaluated with the `nllb()` function, which calculates the negative
log-likelihood for the residuals under the assumption of a binomial distribution.

Within a function, an empty list named 'l_models' is created to hold the summaries of each fit.

## Arguments

The arguments in the function are as follows:

    model  A list that stores the functions of selected models for fitting a   cumulative density function.
    prm    A list that contains the parameter values b1 and b2 of the selected model.
    lista  A list where the first item contains the original data, and items 2 to B+1 contain the resampled data frames.
    B      An integer that determines the number of resamplings.
    nLL    The negative logarithmic likelihood function will be   minimized using the "optim()" function.

## Returns

The function returns a list containing the stored summaries.

## Import from
  optim() from the stats package
  na.omit from the stats package

## Sea also
     Model functions from simodiff package: GoM(), HiM(), LoM(), WeM() and GaM()
     The negative logarithmic likelihood function from simodiff package:nllb
     
## Example

This example uses the `Lperu` dataset, which is included in a `simodiff` package.
The dataset contains three variables: sex, length (cm), and binomial, indicating
reproductive conditions with 0 for inactive and 1 for active reproductive organisms.

First, a list of `models` to be analyzed is created. Next, the initial values of
the parameters are set in `prm`. After that, the frequencies and proportions of
reproductively active organisms are calculated for both the original sample and
the B resamples using the function `simodiff::f_resample()`. Finally, the number
of resamplings, denoted as `B`, must be defined by the researcher.

The negative logarithmic likelihood function will be minimized
using the `optim()` function. The function `simodiff::nllb()` calculates the negative log-likelihood for a binomial distribution.

```{r, echo=FALSE}
load("C:/Users/aguir/simodiff/data/Lperu.rda")
```


```{r, eval = FALSE}
set.seed(16)

# The database
df <- Lperu
df <- df[,-1]    # Sex column removed

# The frequency and proportion of organisms actively reproducing
# are defined across class intervals for the total number of
# organisms within each interval. 

Imin <- (trunc(min(df$Length)/5))*5
Imax <- (ceiling(max(df$Length)/5))*5
bin <- 5   #The width of the range class.

B <- 0    # Number of resamples.
n <- dim(df)[1]

f_resample <- simodiff::resample(df, B, n, Imin, Imax, bin)
f_resample <- na.omit(f_resample)

#  List of `models` to be analyzed
models <- list(GoM=simodiff::GoM, HiM=simodiff::HiM,
                LoM=simodiff::LoM, WeM=simodiff::WeM,
                GaM=simodiff::GaM)

 prm <- list(GoM=c("b1"=38,"b2"=0.1), HiM=c("b1"=38,"b2"=10),
             LoM=c("b1"=38,"b2"=3), WeM=c("b1"=38,"b2"=7),
             GaM=c("b1"=21,"b2"=1.8))
 
 fits <- fit_models(models, prm, lista=f_resample,
                    B, nLL= nllb)
 fits
```

## The function

```{r, }
fit_models <- function(models, prm, lista, B, nLL){
          # The list includes the original and de B resampled data sets.
              B <- B+1 
          # Create an empty list to store the model summaries.
              names_M <- names(models)
              l_models <- sapply(names_M, function(x) NULL)
          # Nested for loop to fit the ith model for jth data set.
            for(i in 1:length(models)){
                  model <- unlist(models[[i]])
                  betas <- unlist(prm[[i]])
              for(j in 1:B) {
                  df <- na.omit(lista[[j]])
                  l_models[[i]][[j]] <- optim(par= betas, fn= nLL,
                                              df= df, model= model)
              }
          }
            return(l_models)
 }

```
