---
title: "freq_mature {simodiff}"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{freq_mature}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(simodiff)
```


The function calculates the absolute frequency of the total number of
organisms **x_total** and the organisms active during reproduction by class
interval **x_active**.

It provides a data frame contains four variables (columns): the class mark `CM`,
the absolute frequency of the total number of organisms `ni`, the  number of
organisms active during reproduction `mi`, and the proportions of reproductive
active organisms in each length class.

This function utilizes the `fn_freq()` function from the `Repbio` package.
![Repbio](https://github.com/Macrurido/Repbio.git)

## Arguments

The arguments in the function are as follows:

    x_total  A numeric vector of the length of total of organisms in the sample
    x_active A numeric vector of the length of reproductive active organisms
    Imin     A numeric value of the shortest organism.
    Imax     A numeric value of the longest organism.
    bin      A numeric value that represents the amplitude of the class interval.

## Returns

The function returns a data frame with the frequencies and proportions of a binomial
variable expressed as a fraction of n; for example, the proportion of active 
organisms to the total number of organisms in the ith class interval.

## See also

fn_freq() from the `Repbio` package

## Import from 
  Repbio::fn_freq

## Example

Two normal random number distributions have been created. For example, the first
distribution represents females who are inactive during reproduction `x_inactive`,
with a sample size (n) of 100, a mean (μ) of 20, and a standard deviation (σ) of 5.
The second distribution represents females who are active during reproduction
`x_active`, with a sample size (n) of 50, a mean (μ) of 40, and a standard deviation
(σ) of 10.

The minimum and maximum values of the size range are defined as `Imin` and `Imax`,
respectively. Additionally, the `bin` is designated arbitrarily with a value of 5.

```{r}
set.seed(16)
x_inactive <- round(rnorm(100, 20,sd=5),2)
x_active <- round(rnorm(50, 40,10),2)
x_total <- c(x_inactive, x_active)

Imin <- (trunc(min(x_total)/5))*5
Imax <- (ceiling(max(x_total)/5))*5
bin <- 5

freq_mature <- freq_mature(x_total, x_active, Imin, Imax, bin)
freq_mature

```

## The function

```{r}
freq_mature <- function(x_total, x_active, Imin, Imax, bin){
                        ni <- Repbio::fn_freq(x_total,Imin,Imax,bin)
                        mi <- Repbio::fn_freq(x_active,Imin,Imax,bin)
               # Proportion reproductive active organisms
                        P_act <- mi[,2]/ni[,2]
                        f_tmp <- cbind(CM= ni[,1],
                                       ni= ni[,2],
                                       mi= mi[,2],
                                       P_act)
                        f_tmp <- as.data.frame(f_tmp)
                        return(f_tmp)
}

```

