---
title: "GaM"
subtitle: "Gamma model"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{GaM}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(simodiff)
```

The Gamma model function uses the `gamma()` function from the `stats`
package to find the value of the cumulative density function of a gamma
distribution with certain shape `b1` and rate parameters `b2`.

`b1` is a numerical value that affects the curve's shape, while `b2` is a
numerical value directly related to the rate. Both are stored in the `prm` list.

## Arguments

The arguments in the function are as follows:

    prm a list that stores the Gamma model's parameter values b1 and b2.
    x   is a numeric vector of the ith class interval.   
    
## Returns

The function outputs a numerical vector with the estimated values.

## Example

In this example, fictitious data are utilized. The variable `x` represents the class
mark, while `b1` is a numerical value that affects the curve's shape, while `b2` is a
numerical value directly related to the rate. Both parameters are stored in the `prm`
vector. The results from the GaM() function are stored in `y_hat`.

To visualize the results, a graph illustrating the relationship between `x` and
`y_hat` is presented; this is not part of the function.
    
```{r, warning=FALSE}
library(ggplot2)

x <- seq(5,70,by=5)
b1 <- 25
b2 <- 1
prm <- c("b1"=b1,"b2"=b2)

y_hat <- GaM(prm, x)
y_hat 

p <- ggplot()+ geom_point(aes(x=x,y=y_hat))
p
```

## The function
```{r}
GaM <- function(prm, x){
  b1 <- prm[1]
  b2 <- prm[2]
  x <- x
  return(stats::pgamma(x, b1, rate = 1/b2))
}
```

