---
title: "HiM"
subtitle: "Hill model"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{HiM}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(simodiff)
```


The Hill model function was implemented to find the value of the cumulative density
function of a Hill distribution with certain shape **b1** and rate parameters **b2**.

 $$p_{i}= \frac{1}{1+^{\left( \frac{b_{1}}{x_{i}} \right)^{b_{2}}}}$$

 Where:

   $p_{i}$ represents a binomial variable expressed as a
           fraction of n; for example, the proportion of active organisms to
           the total number of organisms in the ith class interval.
   $b_{1}$ is the point of inflection of the curve.
   $b_{2}$ is related directly to the width of the interval.
   
## Arguments

The arguments in the function are as follows:

    prm a list that stores the Hill model's parameter values b1 and b2.
    x   is a numeric vector of the ith class interval.   
    
## Returns

The function outputs a numerical vector with the estimated values.

## Example

In this example, fictitious data are utilized. The variable `x` represents the class mark, while `b1` denotes the length at 50% maturity (l50), which is defined as the inflection point of the curve. The variable `b2` is directly related to the width of the interval. Both parameters are stored in the `prm` vector. The results from the HiM() function are stored in `y_hat`.

To visualize the results, a graph illustrating the relationship between `x` and
`y_hat` is presented; this is not part of the function.
    
```{r, warning=FALSE}
library(ggplot2)

x <- seq(5,70,by=5)
b1 <- 38
b2 <- 8
prm <- c("b1"=b1,"b2"=b2)

y_hat <- HiM(prm, x)
y_hat 

p <- ggplot()+ geom_point(aes(x=x,y=y_hat))
p
```

## The function

```{r}
HiM <- function(prm, x){
  b1 <- prm[1]
  b2 <- prm[2]
  x <- x
  return(1/(1+(b1/x)^b2))
}
```

