---
title: "nllb"
subtitle: "Negative log-likelihood for a binomial distribution of residuals"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{nllb}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(simodiff)
```

The function calculates the negative log-likelihood for a binomial
distribution of residuals.

The log-likelihood function, denoted as `nllb`, computes the fitted value `y_hat`
for the *ith* selected model and returns the binomial negative log-likelihood value.

The models included here had the same statistical assumption regarding the errors.
Each model was fit to the data, minimizing the negative value of the log-likelihood
function by using a binomial density probabilistic function (Aguirre-Villaseñor 
et al., 2022).

## Arguments

The arguments in the function are as follows:

    prm    A list that contains the parameter values b1 and b2 of the selected model.
    df     A data frame, it should be organized as follows:
            class mark (MC) in column 1; total number of the sample (ni)
            in column 2; and number of mature organisms (mi) in column 3.
    model  A list that stores the functions of selected models for fitting a cumulative density function.

## Returns
 
The function returns binomial negative log-likelihood value.

## Import from
magrittr %>%
dplyr filter

## Example

The example utilizes the data frame 'df', which consists of the following columns: the first column contains the class mark (MC), the second column lists the total number of samples (ni), the third column indicates the number of organisms active during reproduction (e), and the fourth column shows the binomial frequency of these organisms.

The five models defined in the simodiff program are stored in a list called `model`: Gompertz `GoM`; Hill `HiM`; Logistic `LoM`: Weibull `WeM` and Gamma `GaM`.

To calculate the binomial negative log-likelihood of each model's, the function
`nllb` was incorporated within a for loop, and the results are stored in the `out`
object.

```{r}
x <- seq(11.25,78.75,by=2.5)
ni <- c(0,0,33,46,140,155,128,57,50,31,53,38,16,10,23,12,42,23,38,14,6,0,1,0,0,0,0,0)
mi <- c(0,0,2,0,1,2,10,2,2,2,31,16,11,8,23,10,42,23,38,14,6,0,1,0,0,0,0,0)
fo <- mi/ni
data <- cbind(x,ni,mi,fo)
data <- as.data.frame(data)

models <- list(GoM=simodiff::GoM, HiM=simodiff::HiM, 
               LoM=simodiff::LoM, WeM=simodiff::WeM,
               GaM=simodiff::GaM)

prm <- list(GoM=c("b1"=38,"b2"=0.1), HiM=c("b1"=38,"b2"=10),
            LoM=c("b1"=38,"b2"=5), WeM=c("b1"=38,"b2"=6),
            GaM=c("b1"=21,"b2"=1.8))

out <- rep(NA,length(models))

for(i in 1:length(models)){
    model <- unlist(models[[i]])
    betas <- unlist(prm[[i]])
    out[i] <- nllb(prm=betas, df=data, model)
}
out
```

## The function
```{r}
nllb <- function(prm, df, model){
  # Remove Zero Values
  data <- data %>% dplyr::filter(ni > 0 & mi > 0)
  data <- as.data.frame(data)
  x <- data[,1]
  ni <- data[,2]
  mi <- data[,3]
  y_hat <- model(prm,x)
  # log Binomial coefficients
  lbc<- log(gamma(ni+1))-(log(gamma(ni-mi+1))+log(gamma(mi+1)))
  # Ratio test
  nll <-  -sum(mi*log(y_hat/(1-y_hat))+(ni*log(1-y_hat))+lbc)
  # Return binomial negative log-likelihood
  return(nll)
}

```



