---
title: "resample {simodiff}"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{resample}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(simodiff)
```

This function resamples the organisms in the data frame `df`, which
includes the `Length` and `Binomial` columns, indicating whether each organism is
inactive (0) or active in reproduction (1).

The frequency of mature organisms to the total number of organisms is calculated
for each class mark using the `simodiff::freq_mature` function.

The results are stored in a list, with the first item representing the original data frequencies. The variable `B` defines the number of resamplings to be performed.

## Arguments

The arguments in the function are as follows:
    df   A data frame showing the length and binomial condition indicating
          whether organisms are inactive (0) or actively reproducing (1).
    B    An integer that determines the number of resamplings.
    n    An integer that indicates the number of rows to be included in the
          resampled data frame.
    Imin A numeric value of the shortest organism.
    Imax A numeric value of the longest organism.
    bin  A numeric value that represents the amplitude of the class interval.

## Returns

The function outputs a list where the first item contains the original data, and items 2 to B+1 contain the resampled data frames, with B representing the number of resamplings.

## Seealso
freq_mature() from simodiff package

## Import from
dplyr::sample_n
simodiff::freq_mature

## Example

This example uses the `Lperu` dataset, which is included in a `simodiff` package.
The dataset contains three variables: sex, length (cm), and binomial, indicating
reproductive conditions with 0 for inactive and 1 for active reproductive organisms.

To determine the mature frequency, the minimum and maximum values of the size range are defined as `Imin` and `Imax`, respectively. Additionally, the `bin` value is set to 5 arbitrarily. However, these values could be deffined by the researcher.

The number of resamplings `B` must be deffined by the researcher, whereas `n`
indicates the number of rows to be included in the resampled data frame.


```{r, }
set.seed(16)
library(simodiff)
df <- simodiff::Lperu.rda
df <- df[-1]
Imin <- (trunc(min(df$Length)/5))*5
Imax <- (ceiling(max(df$Length)/5))*5
bin <- 5

B <- 3
n <- dim(df)[1]

f_resample <- resample(df, B, n, Imin, Imax, bin)
f_resample
```

## The function
```{r}
resample <- function(df, B, n, Imin, Imax, bin){
                          r_list <- vector("list", length = B+1)
                    for(i in 1:(B+1)){
                      if(i==1){
                          r_data <- df
                      }else{
                          r_data <- dplyr::sample_n(df, n,replace = T)
                      }
                          x_total <- r_data[,1]
                          tmp <- r_data[r_data[,2] == 1,]
                          x_active <- tmp[,1]
                          r_list[[i]] <- simodiff::freq_mature(x_total, x_active,
                                                              Imin, Imax, bin)
                    }
                          return(r_list)
}

```

